On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-15 6_results_RQ2.tex
Other minor stuff fixed, and comments added, up to §7

>>>>

\sm{This argument is far from being conclusive but it confirms that
  the ten workers that we used in our experiment, and the associated
  cost, can be reduced. 
  Therefore, from the about $\$0.4$ for each document figure mentioned
  in Section~\ref{sec:crowd-judging} we can estimate that only about
  $\$0.3$  for each document are really needed, if not less since more
  efficient methods could be devised.}

### 2016-09-15 7_results_RQ3.tex
Other minor stuff fixed, and comments added, up to §7

@@

\begin{figure}[p]
  \centering
  \includegraphics[width=.6\linewidth]{figs/sysRank_scatter_TREC_med3bestME.pdf}
  \caption{System scores using TREC categories (y-axis) 
    and magnitudes (x-axis) as gains in 
    the nDCG@10 and ERR@10 metrics. There is one dot for each of the 129 systems 
    participating in the TREC-8 ad hoc track, with red dots showing the top-set (see text).
    Magnitudes used are the median of the three units per document that most agree with TREC
    document rankings.
    Kendall's $\tau$ is shown. 
  \label{fig:runs-rerank-median3best}
  }
\end{figure}
\begin{figure}[p]
  \centering
  \includegraphics[width=.6\linewidth]{figs/sysRank_scatter_FAKE_medME3bestME.pdf}
  \caption{As for Figure~\ref{fig:runs-rerank-median3best} but using 
           Sormunen categories (y-axis) and simulated runs as described in the text.
  \label{fig:runs-rerank-median3best-fake}
  }
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=.7\linewidth]{figs/metrics_resample.pdf}
  \caption{Kendall's $\tau$ between system rankings obtained using gains from 
    the judgments and metrics indicated on the x-axis, where magnitudes are randomly
    sampled for each document 1000 times. Compare with $\tau$ in
Figures~\ref{fig:runs-rerank-median3best} and~\ref{fig:runs-rerank-median3best-fake}.
  \label{fig:runs-rerank-resample}
  }
\end{figure}

An alternate explanation for the low $\tau$ values is that gains set as
magnitudes are generally much higher than the gains set by Sormunen's
categories.
From Figure~\ref{fig:ME-distribution} it is apparent that magnitudes
are generally in the range of 2 to 15 (although some are as large as
100 or 1000), whereas using categories as gains the values are 0, 1, 2
or 3. However, because both nDCG and ERR are normalized, this scale
effect is nullified to a degree.
For example, multiplying gains by a constant has no effect on nDCG, and
even altering the category scores using a small exponential or additive
constant has little effect.
Table~\ref{tab:scaling-cats} shows this Kendall's $\tau$ for our 12
topics on the simulated systems using various mappings of Sormunen
categories to gain values, and a mapping of those categories.
The final two rows hint that using gain values from a broad scale,
while preserving document orderings, may alter system rankings,
particularly with nDCG@10, compared with simply using the category
values as gains.
The final row perhaps best represents our magnitude scores, and so goes
partway to explaining the low $\tau$ values in the previous section.

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=.6\linewidth]{figs/sysRank_scatter_TREC_med3bestME.pdf}
  \caption{System scores using TREC categories (y-axis) 
    and magnitudes (x-axis) as gains in 
    the nDCG@10 and ERR@10 metrics. There is one dot for each of the 129 systems 
    participating in the TREC-8 ad hoc track, with red dots showing the top-set (see text).
    Magnitudes used are the median of the three units per document that most agree with TREC
    document rankings.
    Kendall's $\tau$ is shown. 
  \label{fig:runs-rerank-median3best}
  }
\end{figure}
\begin{figure}[tbp]
  \centering
  \includegraphics[width=.6\linewidth]{figs/sysRank_scatter_FAKE_medME3bestME.pdf}
  \caption{As for Figure~\ref{fig:runs-rerank-median3best} but using 
           Sormunen categories (y-axis) and simulated runs as described in the text.
  \label{fig:runs-rerank-median3best-fake}
  }
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=.7\linewidth]{figs/metrics_resample.pdf}
  \caption{Kendall's $\tau$ between system rankings obtained using gains from 
    the judgments and metrics indicated on the x-axis, where magnitudes are randomly
    sampled for each document 1000 times. Compare with $\tau$ in
Figures~\ref{fig:runs-rerank-median3best} and~\ref{fig:runs-rerank-median3best-fake}.
  \label{fig:runs-rerank-resample}
  }
\end{figure}

An alternate explanation for the low $\tau$ values is that gains set as
magnitudes are generally much higher than the gains set by Sormunen's
categories.
From Figure~\ref{fig:ME-distribution} it is apparent that magnitudes
are generally in the range of 2 to 15 (although some are as large as
100 or 1000), whereas using categories as gains the values are 0, 1, 2
or 3. However, because both nDCG and ERR are normalized, this scale
effect is nullified to a degree.
For example, multiplying gains by a constant has no effect on nDCG, and
even altering the category scores using a small exponential or additive
constant has little effect.
\sm{The following sentence is... unclear}Table~\ref{tab:scaling-cats} shows this Kendall's $\tau$ for our 12
topics on the simulated systems using various mappings of Sormunen
categories to gain values, and a mapping of those categories.
The final two rows hint that using gain values from a broad scale,
while preserving document orderings, may alter system rankings,
particularly with nDCG@10, compared with simply using the category
values as gains.
The final row perhaps best represents our magnitude scores, and so goes
partway to explaining the low $\tau$ values in the previous section.
